Finite Complete Suites for CSP Refinement Testing

### 2018-11-13 scp-journal/article/abstract.tex
update

In this paper, two new contributions for model-based testing with
Communicating Sequential Processes (CSP) are presented. For a given CSP
process representing the reference model, test suites checking the
conformance relations trace refinement and failures refinement are constructed, and
their finiteness and completeness (that is, capability to uncover conformity
violations) is proven. While complete test suites for CSP processes have been
previously investigated by several authors, a sufficient condition for their
finiteness is presented here for the first time.
%Moreover, an optimal
%technique for testing the admissibility of an implementation's
%nondeterministic behaviour is described.
It is shown that the test suites are optimal with respect to two
aspects:~(a)~the maximal length of test traces cannot be reduced, and (b)~the
nondeterministic behaviour cannot be tested with smaller or fewer sets of
events, without losing the test suite's completeness property.

>>>>

In this paper, two new contributions for model-based testing with
Communicating Sequential Processes (CSP) are presented. For a given CSP
process representing the reference model, test suites checking the
conformance relations trace refinement and failures refinement are constructed, and
their finiteness and completeness (that is, capability to uncover conformity
violations) is proven. While complete test suites for CSP processes have been
previously investigated by several authors, a sufficient condition for their
finiteness is presented here for the first time.
It is shown that the test suites are optimal with respect to two
aspects:~(a)~the maximal length of test traces cannot be further reduced, and (b)~the
nondeterministic behaviour cannot be tested with smaller or fewer sets of
events, without losing the test suite's completeness property.

### 2018-11-13 scp-journal/article/introduction.tex
update

\subsubsection*{Motivation}

@@

\subsubsection*{Contributions}

@@

Our results complement work in~\cite{DBLP:conf/pts/CavalcantiS17}. There,
fault domains are specified as collections of processes refining a ``most
general'' fault domain member. With that concept, complete test suites may be
finite or infinite. This result gives important insight into the theory of
fault-domain testing for CSP, but we are particularly interested in {\it
finite} suites when it comes to practical application.
While~\cite{DBLP:conf/pts/CavalcantiS17} may require additional criteria to
select tests from still infinite test suites, here, we further restrict fault
domains using a graph representation of processes (originally elaborated for
model checking) to obtain finite test suites.

@@

\subsubsection*{Overview}
In Section~\ref{section:preliminaries}, we present the background
relevant to our work. In Section~\ref{sec:finitecompletefails}, finite
complete test suites for verifying failures refinement are presented. Test
suites checking trace refinement are a simplified version of the former
class; they are presented in Section~\ref{sec:finitecomplete}.
The optimality results are presented in Section~\ref{sec:complexity}, together with further
complexity considerations.
A sample test
suite is presented in Section~\ref{sec:case}. Our results are discussed in
Section~\ref{sec:conc}, where we also conclude. References to related work
are given throughout the paper where appropriate.

>>>>

\subsection{Motivation}

@@

\subsection{Contributions}

@@

Our results complement work 
in~\cite{DBLP:conf/icfem/CavalcantiG07,DBLP:conf/pts/CavalcantiS17}.

@todo -- refer to/ compare to both publications

There,
fault domains are specified as collections of processes refining a ``most
general'' fault domain member. With that concept, complete test suites may be
finite or infinite. This result gives important insight into the theory of
fault-domain testing for CSP, but we are particularly interested in {\it
finite} suites when it comes to practical application.
While~\cite{DBLP:conf/pts/CavalcantiS17} may require additional criteria to
select tests from still infinite test suites, here, we further restrict fault
domains using a graph representation of processes (originally elaborated for
model checking) to obtain finite test suites.

@@

\subsection{Overview}
In Section~\ref{section:preliminaries}, we present the background
relevant to our work. In Section~\ref{sec:finitecompletefails}, finite
complete test suites for verifying failures refinement are presented. Test
suites checking trace refinement are a simplified version of the former
class; they are presented in Section~\ref{sec:finitecomplete}.
The optimality results are presented in Section~\ref{sec:complexity}, together with further
complexity considerations.
A sample test
suite is presented in Section~\ref{sec:case}. Our results are discussed in
Section~\ref{sec:conc}, where we also conclude. References to related work
are given throughout the paper where appropriate.
